Report and Figures

### 2016-11-11 figs.Rmd
loss curve updates

@@

background %>% 
  ggplot(aes(x = nclust, y = I_XY)) +
  geom_path(aes(group = city), color = 'grey', alpha = 0.6) + 
  geom_path(aes(group = city, color = city), data = highlighted) +
  geom_label(aes(label = city, fill = city), data = end_points) +
  theme_light() +
  scale_x_continuous(trans = 'log10', limits = c(1,NA), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0,.5), expand = c(0, 0)) + 
  scale_color_brewer(palette = 'Set1', name = NULL, guide = 'none') +
  scale_fill_brewer(palette = 'Set1', name = NULL, guide = 'none') +
  xlab('Number of clusters (n)') + 
	ylab(expression(I(C[n],Y))) +
  # geom_vline(xintercept=2, alpha = .2) + 
  annotation_logticks(sides = 'b', size = .2)

@@

background %>% 
  ggplot(aes(x = nclust, y = I_XY)) +
  geom_path(aes(group = city), color = 'grey', alpha = 0.6) + 
  geom_path(aes(group = city, color = city), data = highlighted) +
  geom_label(aes(label = city, fill = city), data = end_points) +
  theme_light() +
  scale_x_continuous(trans = 'log10', limits = c(1,NA), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0,.7), expand = c(0, 0)) + 
  scale_color_brewer(palette = 'Set1', name = NULL, guide = 'none') +
  scale_fill_brewer(palette = 'Set1', name = NULL, guide = 'none') +
  xlab('Number of clusters (n)') + 
	ylab(expression(I(C[n],Y))) +
  # geom_vline(xintercept=2, alpha = .2) + 
  annotation_logticks(sides = 'b', size = .2)

>>>>

rects <- highlighted %>% group_by(city) %>% 
	summarise(xmin = 1, ymin = 0, xmax = max(nclust), ymax = max(I_XY))

@@

background %>% 
  ggplot() +
  geom_path(aes(group = city, x = nclust, y = I_XY), color = 'grey', alpha = 0.6) + 
  geom_path(aes(group = city, color = city, x = nclust, y = I_XY), data = highlighted) +
  geom_label(aes(x = nclust, y = I_XY, label = city, fill = city), data = end_points) +
  theme_light() +
  scale_x_continuous(trans = 'log10', limits = c(1,NA), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0,.5), expand = c(0, 0)) + 
  scale_color_brewer(palette = 'Set1', name = NULL, guide = 'none') +
  scale_fill_brewer(palette = 'Set1', name = NULL, guide = 'none') +
  xlab('Number of clusters (n)') + 
	ylab(expression(I(C[n],Y))) +
  # geom_vline(xintercept=2, alpha = .2) + 
  annotation_logticks(sides = 'b', size = .2) +
  geom_rect(data = rects, aes(xmin = xmin,
								ymin = ymin,
								xmax = xmax,
								ymax = ymax,
								group = city,
								color = city),
			  # color = 'grey',
			  alpha = 0,
			  size = 0.25)

@@

filled <- highlighted[,c('nclust','I_XY', 'city')] %>% 
  select(city, I_XY, nclust) %>% 
  ungroup()

background %>% 
  ggplot() +
  geom_path(aes(group = city, x = nclust, y = I_XY), color = 'grey', alpha = 0.6) + 
  geom_path(aes(group = city, color = city, x = nclust, y = I_XY), data = highlighted, size = 1) +
  theme_light() +
  scale_x_continuous(trans = 'log10', limits = c(1,NA), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0,.7), expand = c(0, 0)) + 
  scale_color_brewer(palette = 'Set1', name = NULL, guide = 'none') +
  scale_fill_brewer(palette = 'Set1', name = NULL, guide = 'none') +
  xlab('Number of clusters (n)') + 
	ylab(expression(I(C[n],Y))) +
  # geom_vline(xintercept=2, alpha = .2) + 
  annotation_logticks(sides = 'b', size = .2) +
  # geom_polygon(aes(nclust, I_XY, fill = city, group = city), data = filled, alpha = .15) + 
  geom_rect(data = rects, aes(xmin = xmin,
								ymin = ymin,
								xmax = xmax,
								ymax = ymax,
								group = city,
								color = city),
			  # color = 'grey',
			  alpha = 0,
			  size = 0.3) + 
  geom_label(aes(x = nclust, y = I_XY, label = city, fill = city), data = end_points)
